Evaluating Storage Systems for Scientific Data in the Cloud

### 2014-04-28 paper.tex
bare journal

\documentclass{sig-alternate}
\usepackage{comment}
\usepackage{listings}
\usepackage{pgf}
\usepackage{amsmath}
\usepackage{subfigure}
\usepackage{tikz}

@@

@@

%\newif\ifdraft
%\drafttrue
%%\draftfalse
%\ifdraft
% \newcommand{\katznote}[1]{ {\textcolor{blue}    { ***Dan:      #1 }}}
% \newcommand{\ketanote}[1]{{\textcolor{orange}    { ***Ketan:      #1 }}}
% \newcommand{\note}[1]{ {\textcolor{red}    {\bf #1 }}}
%\else
% \newcommand{\katznote}[1]{}
% \newcommand{\ketanote}[1]{}
% \newcommand{\note}[1]{}
%\fi
%% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
\title{Evaluating Storage Systems for Scientific Data in the Cloud}
\author{
\alignauthor
  Ketan Maheshwari$^\ast$ Justin M. Wozniak$^\ast$
  Hao Yang$^\ddagger$ Daniel S. Katz$^\ast\dagger$ \\
  Matei Ripeanu$^\ddagger$  
  Victor Zavala$^\ast$ Michael Wilde$^\ast\dagger$ \\
%  ~\\
  \begin{tabular}{ccc}
      \hspace{.14\linewidth} & \hspace{.14\linewidth} & \hspace{.14\linewidth}\\
      $^\ast$\affaddr{Mathematics and Computer Science Division}  & 
      $^\dagger$\affaddr{Computation Institute}  &
      $^\ddagger$\affaddr{Dept. of Electrical and Computer Eng.} \\
      \affaddr{Argonne National Laboratory} & \affaddr{University of Chicago} & \affaddr{University of British Columbia} \\
      \affaddr{Argonne, IL USA} & \affaddr{Chicago, IL USA} & \affaddr{Vancouver, Ca}\\
      \affaddr{ketan,wozniak,zavala,wilde@mcs.anl.gov} & \affaddr{dsk@ci.uchicago.edu} & \affaddr{yanghao0614,matei@ece.ubc.ca} \\
  \end{tabular}
}

@@

%TODO: Summarize conclusions/lessons
%
\end{abstract}

\keywords{HPC, parallel computing, cloud, global file systems}

@@

\bibliographystyle{abbrv}
\bibliography{refshort}
\end{document}

>>>>

\documentclass[10pt,journal,cspaper,compsoc]{IEEEtran}
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  \usepackage[dvips]{graphicx}
\fi

\usepackage{comment}
\usepackage{listings}
\usepackage{pgf}
\usepackage{amsmath}
\usepackage{subfigure}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}

@@

\definecolor{darkgreen}{rgb}{0,0.7,0}

\newif\ifdraft
\drafttrue
%\draftfalse
\ifdraft
 \newcommand{\katznote}[1]{ {\textcolor{blue}    { ***Dan:      #1 }}}
 \newcommand{\ketanote}[1]{{\textcolor{orange}    { ***Ketan:      #1 }}}
 \newcommand{\note}[1]{ {\textcolor{red}    {\bf #1 }}}
\else
 \newcommand{\katznote}[1]{}
 \newcommand{\ketanote}[1]{}
 \newcommand{\note}[1]{}
\fi
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\begin{document}
% can use linebreaks \\ within to get better formatting as desired
\title{Evaluating Storage Systems for Scientific Data in the Cloud}
% \title{Evaluation of global-scale programming and data storage techniques
%        in cloud computing}

\author{\IEEEauthorblockN{Ketan Maheshwari\IEEEauthorrefmark{1},
Justin M. Wozniak\IEEEauthorrefmark{1},
Hao Yang\IEEEauthorrefmark{2},\\
Daniel S. Katz\IEEEauthorrefmark{3},
Matei Ripeanu\IEEEauthorrefmark{2},
Victor Zavala\IEEEauthorrefmark{3},
Michael Wilde\IEEEauthorrefmark{1}\IEEEauthorrefmark{3}\\
\IEEEauthorblockA{
\IEEEauthorrefmark{1}MCS Division, Argonne National Laboratory, Argonne, IL 60439}\\
\IEEEauthorrefmark{2}Department of Electrical and Computer Engineering,  University of British Columbia\\
\IEEEauthorrefmark{3}Computation Institute,  University of Chicago \& Argonne National Laboratory}
}

@@

%TODO: Summarize conclusions/lessons
%
\end{abstract}
\begin{IEEEkeywords}
HPC, parallel computing, cloud, storage systems
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

@@

\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}
